---
title: "The migbirdHIP Workflow"
output:
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The migbirdHIP Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Table of Contents

-   [Introduction](#introduction)
    -   [Installation](#installation)
        -   [Releases](#releases)
    -   [Load](#load)
    -   [Functions overview](#functions-overview)
    -   [Example data](#example-data)
-   [Part A: Data Import and Cleaning](#part-a-data-import-and-cleaning)
    -   [fileRename](#filerename)
    -   [fileCheck](#filecheck)
    -   [read_hip](#read_hip)
    -   [qualityMessages](#qualitymessages)
    -   [glyphCheck](#glyphcheck)
    -   [shiftCheck](#shiftcheck)
    -   [clean](#clean)
    -   [issueCheck](#issuecheck)
    -   [duplicateFinder](#duplicatefinder)
    -   [duplicateFix](#duplicatefix)
    -   [bagCheck](#bagcheck)
    -   [proof](#proof)
    -   [correct](#correct)
-   [Part B: Data Visualization and Tabulation](#part-b-data-visualization-and-tabulation)
    -   Visualization
        -   [duplicatePlot](#duplicateplot)
        -   [errorPlotFields](#errorplotfields)
        -   [errorPlotStates](#errorplotstates)
        -   [errorPlotDL](#errorplotdl)
    -   Tabulation
        -   [pullErrors](#pullerrors)
        -   [errorTable](#errortable)
-   [Part C: Writing Data and Reports](#part-c-writing-data-and-reports)
    -   [write_hip](#write_hip)
    -   [writeReport](#writereport)

## Introduction {#introduction}

The `migbirdHIP` package was created by the U.S. Fish and Wildlife Service (USFWS) to process, clean, and visualize Harvest Information Program (HIP) registration data.

### Installation {#installation}

The package can be installed from the USFWS GitHub repository using:

```{r, install, eval = FALSE}
pak::pak("USFWS/migbirdHIP")
```

#### Releases {#releases}

To install a past release, use the example below and substitute the appropriate version number. Releases are documented in the [README](https://github.com/USFWS/migbirdHIP/blob/main/README.md#releases).

```{r, releases, eval = FALSE}
pak::pak("USFWS/migbirdHIP@v2026.0.0")
```

### Load {#load}

Load `migbirdHIP` after installation. The package will return a startup message with the version you have installed and what season of HIP data the package version was intended for.

```{r setup}
library(migbirdHIP)
```

### Functions overview {#functions-overview}

The flowchart below is a visual guide to the order in which functions are used. Some functions are only used situationally and some issues with the data cannot be solved using a function at all. The general process of handling HIP data is demonstrated in the flowchart; every exported function in the `migbirdHIP` package is included in it and the vignette.

```{r flowchart_svg, echo = FALSE, fig.cap = "Overview of migbirdHIP functions in a flowchart format.", out.width = "100%", dev = "svg", fig.align = "center"}
knitr::include_graphics(
  paste0(here::here(), "/man/figures/migbirdHIP_flowchart.svg"))
```

### Example data

Example data are included in the `migbirdHIP` R package in two formats. Raw data files are provided with fake names, addresses, and other registration values, mainly to include examples and tests for reading in data. In addition, small data objects derived from the fake registrations are exported to users.

#### Raw data

Raw data in the form of fake HIP registration data files were generated with `data-raw/create_fake_HIP_data.R`. The 49 files (one for each state) are stored in the `migbirdHIP` R package under `inst/extdata/`. You can test [read_hip()](#read_hip) with the files in this directory. 

#### Exported data

There are 7 data objects stored in `/data/` as `.rda` files. Users can call these objects by name (e.g., `DF_TEST_MINI`) and query their documentation (e.g., `?DF_TEST_MINI`) from the console after loading `migbirdHIP`. 

The biggest object is `DF_TEST_MINI` with ~1,600 rows. This tibble represents "raw data" and doesn't contain the `record_key` field. The other 6 objects all begin with the `DF_TEST_TINI_` prefix and represent HIP data at various points during pre-processing. They are small, containing only 3 rows per object, but exhibit properties that are expected from each intermediate output. For example, `DF_TEST_TINI_PROOFED` contains the `errors` field. Users can run these objects in `migbirdHIP` package functions.

List of exported data objects:

- `DF_TEST_MINI`
- `DF_TEST_TINI_READ`
- `DF_TEST_TINI_CLEANED`
- `DF_TEST_TINI_CURRENT`
- `DF_TEST_TINI_DEDUPED`
- `DF_TEST_TINI_PROOFED`
- `DF_TEST_TINI_CORRECTED`

## Part A: Data Import and Cleaning {#part-a-data-import-and-cleaning}

### fileRename {#filerename}

The `fileRename()` function renames non-standard file names to the standard format. We expect a file name to be a 2-letter capitalized state abbreviation followed by YYYYMMDD (indicating the date data were submitted).

Some states submit files using a 5-digit file name format, containing 2 letters for the state abbreviation followed by a 3-digit Julian date. To convert these 5-digit filenames to the standard format (a requirement to read data properly with [read_hip()](#read_hip)), supply `fileRename()` with the directory containing HIP data. File names will be automatically overwritten with the YYYYMMDD format date corresponding to the submitted Julian date.

This function also converts lowercase state abbreviations to uppercase.

The current hunting season year must be supplied to the `year` parameter to accurately convert dates.

```{r rename, eval = FALSE}
fileRename(path = "C:/HIP/raw_data/DL0901", year = 2026)
```

### fileCheck {#filecheck}

Check if any files in the input folder have already been written to the processed folder using `fileCheck()`.

```{r filecheck, eval = FALSE}
fileCheck(
  raw_path = "C:/HIP/raw_data/DL0901/",
  processed_path = "C:/HIP/corrected_data/"
)
```

### read_hip {#read_hip}

Read HIP data from fixed-width `.txt` files using `read_hip()`. Files must adhere to a 10-character naming convention to successfully be read in (2-letter capitalized state abbreviation followed by `YYYYMMDD`); if files were submitted with a 5-digit format or lowercase state abbreviation, run [fileRename()](#filerename) first.

In the example below, we will use the default `read_hip()` settings to read in all of the fake HIP data files from an internal package directory (read more in the [example data](#example-data) section). All other examples in this vignette will use `C:/` drive examples for clarity.

```{r, readhip}
raw_data <- read_hip(paste0(here::here(), "/inst/extdata/DL0901/"))
```

#### The `read_hip()` function allows data to be read in for:

-   All states (e.g., `state = NA`, the default).
-   A specific state (e.g., `state = "DE"`).
-   A specific download (e.g., `season = FALSE`, the default; `path` must be to the download's subdirectory).
-   An entire season (e.g., `season = TRUE`, and `path` is to the directory containing all download subdirectories).

Use `unique = TRUE` to read in a frame without exact duplicates, or `unique = FALSE` to read in all registrations including exact duplicates. **Important:** the `record_key` field is not created for `unique = FALSE`, which is required in some following steps (e.g., `duplicateFix()`, `proof()`).

Data are read in an expected format beginning with the `title` field and ending with `email` field. Additional fields are created by `read_hip()`: `dl_state`, `dl_date`, `source_file`, `dl_cycle`, `dl_key`, `record_key`.

#### The `read_hip()` function does NOT read in data:

-   From subfolders named `"hold"`, `"permit"`, or `"lifetime"`.
-   Permit and lifetime HIP registrations must be read in and processed in a different workflow than the one outlined in this vignette.

#### The `read_hip()` function fails if:

-   The state abbreviation in the file name is not found in the list of 49 continental US states.
-   The date in the file name is formatted incorrectly.

#### The `read_hip()` function returns a message if:

-   Blank files are found in the directory.

### qualityMessages {#qualitymessages}

#### The `qualityMessages()` function returns a message if:

-   `NA` values are detected in one or more ID fields (`firstname`, `lastname`, `state`, `birth_date`) for \>10% of a file and/or \>100 registrations.
-   All emails are missing from a file.
-   Test records are found.
-   Any registration has a `0` in every bag field.
-   Any registration has an `NA` in every bag field.
-   Any registration contains a bag value that is not a 1-digit number.
-   For presumed solo permit did-not-hunts; if any Oregon or Washington `hunt_mig_birds` registration value does not equal `2` when non-permit bags are `0` and one of `band_tailed_pigeon`, `brant`, and/or `seaduck` is `2`.
-   Any `registration_yr` is not equal to `REF_CURRENT_SEASON` or `REF_CURRENT_SEASON + 1`.
-   Any file contains a `state` value not equal to `dl_state` that makes up 10% or more of the file's registrations.
-   Any inter-state duplicates are detected.

### glyphCheck {#glyphcheck}

During pre-processing, R may throw an error that says something like "invalid UTF-8 byte sequence detected". The error usually includes a field name but no other helpful information. The `glyphCheck()` function identifies values containing non-UTF-8 glyphs/characters and prints them with the source file in the console so they can be edited.

```{r glyphCheck}
glyphCheck(raw_data)
```

### shiftCheck {#shiftcheck}

Find and print any rows that have a line shift error with `shiftCheck()`.

```{r shiftCheck}
shiftCheck(raw_data)
```

### clean {#clean}

The `clean()` function performs data cleaning and filters out bad registrations.

```{r, clean}
clean_data <- clean(raw_data)
```

#### Registrations are dropped if:

-   Any bag value is not a 1-digit number.
-   Every bag field is `NA` or `0`.
-   A test record is detected:
    -   `firstname` and `lastname` are `"TEST"`.
    -   `lastname` is `"INAUDIBLE"`.
    -   `firstname` is one of: `"INAUDIBLE"`, `"BLANK"`, `"USER"`, `"TEST"`, or `"RESIDENT"`.
-   There is missing contact/identification information:
    -   `NA` value in `firstname`, `lastname`, `state`, or `birth_date`.
    -   `NA` for `address` *and* `email`.
    -   `NA` for `email` *and* `city` and/or `zip`.

#### Changes include:

-   `firstname`
    -   Change to uppercase.
    -   If a suffix value is detected (e.g., `JR`, `SR`, `1ST` to `20TH`, and `1` to `20` in Roman numerals, excluding `XVIII`) delete it. 
    -   Delete white space around string.
-   `lastname`
    -   Change to uppercase.
    -   If a suffix value is detected (e.g., `JR`, `SR`, `1ST` to `20TH`, and `1` to `20` in Roman numerals, excluding `XVIII`) delete it. 
    -   Delete white space around string.
-   `suffix`
    -   Change to uppercase.
    -   If a suffix is detected in `firstname` or `lastname`, replace the `suffix` with that value. Values that are searched for include `JR`, `SR`, `1ST` to `20TH`, and `1` to `20` in Roman numerals, excluding `XVIII`. 
    -   Periods and commas are deleted.
-   `zip`
    -   Remove ending hyphen from zip codes with only 5 digits.
    -   Remove ending `0` from zip codes with 10 digits.
    -   Insert a hyphen in continuous 9-digit zip codes.
    -   Insert a hyphen in 9-digit zip codes with a middle space.
    -   Delete trailing `-0000` and `-____`.
-   `hunt_mig_birds`
    -   For Oregon and Washington, if a registration's `hunt_mig_birds` value is `0` and if `band_tailed_pigeon`, `brant`, or `seaduck` is `2`, change `hunt_mig_birds` value from `0` to `2`.
-   `band_tailed_pigeon`
    -   If any permit file states submitted a `2` for `band_tailed_pigeon`, change the `2` to a `0`.
-   `cranes`
    -   If any permit file states submitted a `2` for `cranes`, change the `2` to a `0`.

In addition to the changes listed above, the internal `zipCheck()` function returns a message from `clean()` if zip codes are detected that do not correspond to provided state of residence for \>10% of a file and/or \>100 registrations.

### issueCheck {#issuecheck}

The `issueCheck()` function assesses the validity of a registration's `issue_date` value. It does this based on the current hunting season's HIP issue window start date and end date (not season open and close dates) for the state in which the registration was issued. A plot is automatically returned for past and future registrations. The plot is skipped by default, so to make one, specify `plot = TRUE`.

```{r, issuecheck, eval = F}
current_data <- issueCheck(clean_data, year = 2026, plot = FALSE)
```

```{r, createcurrent, include = F}
current_data <- clean_data
```

#### Criteria evaluated and changes made:

-   **Past registration:** a registration's `issue_date` is before the start date of HIP issuance for its state; these registrations are filtered out.
-   **Overlap registration:** registrations from 2-season states with an `issue_date` between the start of next season's issue start and this season's issue end fall into the `"overlap"` category; these registrations are assigned `"current"` if `registration_yr` is equal to `year` or `"future"` if `registration_yr` is `year + 1`.
-   **Current registration:** a registration's `issue_date` falls between the start and end dates of HIP issuance for its state; `registration_yr` is overwritten with `year`.
-   **Future registration:** a registration has an `issue_date` after the last day of issuance for its state for this season AND the `issue_date` falls between the projected issue start and end dates for next season; the `registration_yr` is changed to `year + 1`.
-   **Invalid registration:** a registration's `issue_date` does not fall in the issue window for this season or next season; the date falls in the gap between issue windows. These registrations are filtered out.
-   **Bad `issue_date`:** a registration's `issue_date` cannot be evaluated, likely because it's formatted incorrectly or is illogical; these registrations are filtered out.
-   Return message if any registration's `issue_date` falls after the file was submitted.

### duplicateFinder {#duplicatefinder}

The `duplicateFinder()` function finds hunters that have more than one registration. Registrations are grouped by `firstname`, `lastname`, `state`, `birth_date`, `dl_state`, and `registration_yr` to identify unique hunters. If the same hunter has 2 or more registrations, the fields that are not identical are counted and summarized.

Plot the duplicates with [duplicatePlot()](#duplicateplot).

```{r findDuplicates_tbl}
duplicateFinder(current_data)
```

### duplicateFix {#duplicatefix}

We sometimes receive multiple HIP registrations per person which must be resolved by `duplicateFix()`. Duplicates are identified when more than one registration has the same `firstname`, `lastname`, `state`, `birth_date`, `dl_state`, and `registration_yr`. Only 1 HIP registration per hunter per state can be kept. For in-line permit states (`r unique(migbirdHIP:::REF_PMT_INLINE$dl_state)`), permit records are submitted separately from HIP registrations. Multiple permits are allowed. We differentiate `HIP` and `PMT` records in in-line permit states by checking the values in non-permit species fields (`ducks_bag`, `geese_bag`, `dove_bag`, `woodcock_bag`, `coots_snipe`, and `rails_gallinules`); HIP registrations contain non-zero values in those fields, but permit records always have `0` values.

```{r, duplicateFix}
deduplicated_data <- duplicateFix(current_data)
```

To decide which HIP registration to keep from a group, we follow a series of logical steps.

#### For sea duck and brant states:

These states include: `r paste0(migbirdHIP:::REF_STATES_SD_BR, collapse = ", ")`

1.  Keep registration(s) with the most recent issue date.
2.  Exclude registrations with all `1` values or all `0` values in bag fields from consideration.
3.  Keep any registrations that have a `2` for either `brant` or `seaducks` (for sea duck *and* brant states), or `2` for `seaducks` (Maine only).
4.  If more than one registration remains, choose to keep one randomly.

#### For HIP registrations from in-line permit states and all other states:

These states include: `r paste0(migbirdHIP:::REF_ABBR_49_STATES[!migbirdHIP:::REF_ABBR_49_STATES %in% c(migbirdHIP:::REF_STATES_SD_BR, migbirdHIP:::REF_STATES_SD_ONLY)], collapse = ", ")`

1.  Keep registration(s) with the most recent issue date.
2.  Exclude registrations with all  `1` values or all `0` values in bag fields from consideration, if possible.
3.  If more than one registration remains, choose to keep one randomly.

A new field called `record_type` is added to the data after the above deduplication process. Every HIP registration is labeled `HIP`. Registrations from in-line permit states (Washington and Oregon) can be labeled `HIP` or `PMT`.

### bagCheck {#bagcheck}

The `bagCheck()` function searches for values that are not typical or expected in all species group fields. If a value outside of the normal range is detected, an output tibble is created. Each row in the output contains the state, species, unusual value, and a list of the normal values we would expect. If a value for a species group is provided that doesn't match anything in our records, the output will show `NA` values in the `expected_bag_value` column. These species do not have a hunting season in the reported states.

In-line permit records are not included in this check, to prevent `ducks_bag = "0"` values from popping up when we know those don't count.

```{r, bagCheck}
bagCheck(deduplicated_data)
```

### proof {#proof}

We run `proof()` to check the data for errors. The season's start year must be supplied to the `year` parameter (e.g., `year = 2026` for the 2026-2027 hunting season). This helps to check values in `registration_yr` and `birth_date`. The output of the `proof()` function contains a new field called `errors`.

The fields proofed for errors include `title`, `firstname`, `middle`, `lastname`, `suffix`, `address`, `city`, `state`, `zip`, `birth_date`, `hunt_mig_birds`, `registration_yr`, and `email`.  When values are found to be irregular, the field name(s) is/are added to `errors`. The `errors` field pastes all of the registration's errors together as a hyphen-delimited string; a row can have zero errors (e.g., `NA`), one error (e.g., `"zip"`), two errors (e.g., `"suffix-zip"`), three errors (e.g., `"suffix-address-zip"`), etc; up to all 12 field names.

Note that no actual corrections or data changes take place as a result of the `proof()` function. 

```{r, proof}
proofed_data <- proof(deduplicated_data, year = 2026)
```

#### What gets flagged in the `errors` field and why:

-   `"title"` 
    -   If `title` is not one of: `NA`, `0`, `1` or `2`.
    -   If common first names are assigned the wrong title.
-   `"firstname"`
    -   `firstname` contains anything other than letters, apostrophe(s), space(s), and/or hyphen(s).
    -   `firstname` contains less than 2 letters.
    -   `firstname` contains `"AKA"`.
-   `"middle"` if `middle` is not exactly 1 letter or `NA`.
-   `"lastname"`
    -   `lastname` contains anything except letters, apostrophe(s), space(s), hyphen(s), and/or period(s).
    -   `lastname` contains less than 2 letters.
-   `"suffix"`
    -   `suffix` should be one of: `I, II, III, IV, V, VI, VII, VIII, IX, X, XI, XII, XIII, XIV, XV, XVI, XVII, XIX, XX, 1ST, 2ND, 3RD, 4TH, 5TH, 6TH, 7TH, 8TH, 9TH, 10TH, 11TH, 12TH, 13TH, 14TH, 15TH, 16TH, 17TH, 18TH, 19TH, 20TH, JR, SR`.
    -   Note that `XVIII` is excluded (exceeds 4 character limit).
-   `"address"` if `address` contains a `|`, tab, or non-UTF8 character.
-   `"city"`
    -   `city` contains anything other than letters, space(s), hyphen(s), apostrophe(s), and/or period(s).
    -   `city` contains less than 3 letters.
-   `"state"` 
    -   If `state` is not contained in the following list of abbreviations for US states and territories and Canadian provinces and territories: `r paste0(c(migbirdHIP:::REF_ABBR_49_STATES, migbirdHIP:::REF_ABBR_USA, migbirdHIP:::REF_ABBR_CANADA), collapse = ", ")`.
-   `"zip"`
    -   If a registration's `address` doesn't have a `zip` that should be in their reported address `state` of residence.
    -   If the fist 5 digits of `zip` are not in `REF_ZIP_CODE$zipcode` at all.
-   `"birth_date"`
    -   If the date is formatted poorly (per `REGEX_DATE_FORMAT`).
    -   If the date can't be parsed by `lubridate::mdy()`.
    -   If the date is later than today.
    -   If the date is earlier than `09/01/(REF_CURRENT_SEASON - 100)`.
-   `"hunt_mig_birds"` if not equal to `1` or `2`.
-   `"registration_yr"` if not equal to the current season.
-   `"email"`
    -   `email` does not match universally accepted email regex (see `REGEX_EMAIL`).
    -   `email` is obfuscative:
        -   e.g., `none@gmail.com`, `nottoday@gmail.com`, `fake.fake@gmail.com`, `n@a.com`, `x@y.com`, `brian@na.com`, etc (see `REGEX_EMAIL_OBFUSCATIVE_LOCALPART`, `REGEX_EMAIL_OBFUSCATIVE_DOMAIN`, and `REGEX_EMAIL_OBFUSCATIVE_ADDRESS`).
        -   A repeated character is detected, e.g. `aaa@a.com` (see `REGEX_EMAIL_REPEATED_CHAR`).
        -   The domain is `tpwd.texas.gov` or some variation (see `REGEX_EMAIL_OBFUSCATIVE_TPWD`).
        -   A `walmart.com` domain is preceded by only numbers (see `REGEX_EMAIL_OBFUSCATIVE_WALMART`).
    -   `email` is longer than 100 characters.
    -   A common domain name (e.g., gmail, yahoo) has a common typo.
    -   A common domain name doesn't have a matching top-level domain (e.g., `gmail.net` or `hotmail.gov`).
    -   The address has a bad top-level domain (e.g., `.comcom`, `.ccom`, etc).
    -   The email is missing a top-level domain.
    -   The top-level domain period is missing (e.g., `gmailcom`).

### correct {#correct}

Data can be corrected by running the `correct()` function. Users must provide the season's start year to the `year` parameter (e.g., `year = 2026` for the 2026-2027 hunting season).

```{r correct}
corrected_data <- correct(proofed_data, year = 2026)
```

#### Changes and corrections include:

-   `title` is changed to `NA` if `"title"` is in the `errors` field.
-   `middle` is changed to `NA` if `"middle"` is in the `errors` field.
-   `suffix` is changed to `NA` if `"suffix"` is in the `errors` field.
-   `email`
    -   Add endings to common domains if missing (e.g. `@gmail` would become `@gmail.com`), for domains including:
        -   `gmail, yahoo, hotmail, aol, icloud, comcast, outlook, sbcglobal, att, msn, live, bellsouth, charter, ymail, me, verizon, cox, earthlink, protonmail, pm, mail, duck, ducks`.
    -   Add top-level domain period(s) if:
        -   Missing before `com, net, edu, gov, org`.
        -   Missing in `navymil, mailmil, armymil`; add multiple periods if missing to `usnavymil, usafmil, usarmymil, usacearmymil`.
-   `errors` is updated by re-running `proof()` inside of `correct()`.

## Part B: Data Visualization and Tabulation {#part-b-data-visualization-and-tabulation}

### duplicatePlot {#duplicateplot}

Plot duplicates with `duplicatePlot()`.

```{r, duplicatePlot, fig.cap = "Figure 1. Plot of types of duplicates.", fig.width = 6, fig.height = 3.5, dpi = 300, out.width = 500, fig.align = "center"}
duplicatePlot(current_data)
```

### errorPlotFields {#errorplotfields}

The `errorPlotFields()` function can be run on all states...

```{r errorfieldsplotall, fig.cap = "Figure 2. Plot of all location's errors by field name.", fig.width = 6, fig.height = 3.6, dpi = 300, out.width = 500, fig.align = "center"}
errorPlotFields(proofed_data, loc = "all", year = 2026)
```

... or it can be limited to just one.

```{r errorfieldsplotla, fig.cap = "Figure 3. Plot of Louisiana's errors by field name.", fig.width = 6, fig.height = 3.6, dpi = 300, out.width = 500, fig.align = "center"}
errorPlotFields(proofed_data, loc = "LA", year = 2026)
```

It is possible to add any `ggplot2` components to these plots. A plot can be altered with `facet_wrap` using either `dl_cycle` or `dl_date`. The example below demonstrates how this package's functions can interact with `tidyverse` and shows an example of an `errorPlotFields` with `facet_wrap` (using a subset of 4 download cycles).

```{r errorfieldsfacet, eval = FALSE}
errorPlotFields(
  hipdata2025 |>
    filter(str_detect(dl_cycle, "0800|0901|0902|1001")),
    year = 2026) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0, hjust = 1),
    legend.position = "bottom") +
  facet_wrap(~dl_cycle, ncol = 2)
```

### errorPlotStates {#errorplotstates}

The `errorPlotStates()` function plots error proportions per state. A threshold value must be set to only view states above a certain proportion of error (in the example below, `threshold = 0.05` indicates an error tolerance of 5%). Bar labels are error counts.

```{r errorplotstates, fig.cap = "Figure 4. Plot of proportion of error by state.", fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center"}
errorPlotStates(proofed_data, threshold = 0.05)
```

### errorPlotDL {#errorplotdl}

This function should not be used unless you want to visualize an entire season of data. The `errorPlotDL()` function plots proportion of error per download cycle over the course of the hunting season. Location may be specified with the `loc` parameter to see a particular state over time.

```{r errorPlotDL, eval = FALSE}
errorPlotDL(hipdata2025, loc = "MI")
```

```{r errorplotdl_example, echo = FALSE, fig.cap = "errorPlot_dl example output", out.width = "70%", fig.align = "center"}
knitr::include_graphics(paste0(here::here(), "/man/figures/errorPlot_dl.png"))
```

### pullErrors {#pullerrors}

The `pullErrors()` function can be used to view all of the actual values that were flagged as errors in a particular field. In this example, we find that the `suffix` field contains several values that are not accepted.

```{r pullerrors}
pullErrors(proofed_data, field = "suffix")
```

Running `pullErrors()` on a field that has no errors will return a message.

```{r pullerrors2}
pullErrors(proofed_data, field = "dove_bag")
```

### errorTable {#errortable}

The `errorTable()` function returns error data as a tibble, which can be assessed as needed, or exported to create records of download cycle errors. The basic function reports errors by both location and field.

```{r errortable1}
errorTable(proofed_data)
```

Errors can be reported by only location by turning off the `field` parameter.

```{r errortable2}
errorTable(proofed_data, field = "none")
```

Errors can be reported by only field by turning off the `loc` parameter.

```{r errortable3}
errorTable(proofed_data, loc = "none")
```

Location can be specified using one of the 49 contiguous state abbreviations.

```{r errortable4}
errorTable(proofed_data, loc = "CA")
```

Field can be specified (one of: `"all"`, `"none"`, `"title"`, `"firstname"`, `"middle"`, `"lastname"`, `"suffix"`, `"address"`, `"city"`, `"state"`, `"zip"`, `"birth_date"`, `"hunt_mig_birds"`, `"registration_yr"`, `"email"`).

```{r errortable5}
errorTable(proofed_data, field = "suffix")
```

Total errors for a location can be pulled.

```{r errortable6}
errorTable(proofed_data, loc = "CA", field = "none")
```

Total errors for a field in a particular location can be pulled.

```{r errortable7}
errorTable(proofed_data, loc = "CA", field = "dove_bag")
```

## Part C: Writing Data and Reports {#part-c-writing-data-and-reports}

### write_hip {#write_hip}

After the data have been corrected, the data are ready to be written out. Use `write_hip()` to do final processing to the data, which includes 1) adding in FWS strata and 2) setting `NA` values to blank strings. The `write_hip()` function will fail if there is an `NA` in `dl_state` or if there is an `NA` in `dl_date`. It will also fail if any value exceeds the database character limits (see `failWidths()` helper function). 

If `split = FALSE`, the final table will be saved as a single `.csv` to your specified path. If `split = TRUE` (default), one `.csv` file per each input `.txt` source file will be written to the specified directory.

The `type` argument helps apply additional checks for permits; supply `"HIP"` for HIP data from a regular download, or `"CR"` or `"BT"` for separate permit file records. If `type = "HIP"`, writing data will fail if there are more `record_type = "PMT"` records in the `corrected_data` than `record_type = "HIP"` records.

```{r, writecsv, eval = FALSE}

write_hip(
  corrected_data, 
  path = "C:/HIP/processed_data/", 
  type = "HIP", 
  split = TRUE)

```

### writeReport {#writereport}

The `writeReport()` function can be used to automatically generate an R markdown document with figures, tables, and summary statistics. This can be done at the end of a download cycle.

```{r, writerpt, eval = FALSE}

writeReport(
  raw_path = "C:/HIP/DL0901/",
  temp_path = "C:/HIP/corrected_data",
  year = 2026,
  dl = "0901",
  dir = "C:/HIP/dl_reports",
  file = "DL0901_report")
```
