---
title: "The migbirdHarvestData Workflow"
package: migbirdHarvestData
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The migbirdHarvestData Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Table of Contents

- [Introduction](#introduction)
- [Stage 1: Import Data](#stage-1-import-data)
    - [compile](#compile)
    - [compile_to_utf8](#compile_to_utf8)
    - [tidy](#tidy)
    - [proof](#proof)
- [Stage 2: Visualize Data](#stage-2-visualize-data)
    - [errorPlot_fields](#errorplot_fields)
    - [errorPlot_states](#errorplot_states)
    - [findDuplicates](#findduplicates)
    - [outOfStateHunters](#outofstatehunters)
    - [youthHunters](#youthhunters)
- [Stage 3: Explore Errors](#stage-3-explore-errors)
    - [errorTable](#errortable)
    - [pullErrors](#pullerrors)
    - [redFlags](#redflags)
- [Stage 4: Correct and Compare](#stage-4-correct-and-compare)
    - [correct](#correct)
- [Troubleshooting](#troubleshooting)

## Introduction

The migbirdHarvestData package provides an easy-to-use automated workflow for the U.S. Fish and Wildlife Service to wrangle, tidy, and visualize Harvest Information Program data.

The package can be installed using:
```{r, install, message = FALSE, eval = FALSE}
library(devtools)
install_github("USFWS/migbirdHarvestData")
```


## Stage 1: Import Data

### compile

The first step is to import .txt files containing harvest data. To do this, we attempt to use the `compile` function.

```{r, compile}
library(migbirdHarvestData)

DL1202 <- compile(path = "C:/HIP/DL_1202")
```

The error message above tells us that `compile` did not work because the files contained in the directory are not all encoded as UTF-8. We are provided a tibble of paths to .txt files that threw the error with additional information about their non-UTF-8 encodings. In this example, Latin-1 (ISO-8859-1) and Latin-2 (ISO-8859-2) character sets (which include letters with accents such as ê and á) were the reason the files in the directory were not compatible with the function.

To remedy the situation, we use a different function, `compile_to_utf8`.

### compile_to_utf8

Encoding issues are a nuisance, but `compile_to_utf8` will identify and convert non-UTF-8 text files before importing from them into R from the supplied directory. Please note that this function will overwrite existing files but no changes to the data will occur.

```{r, compileutf}
DL1202_utf8 <- compile_to_utf8(path = "C:/HIP/DL_1202")
```

### tidy

After data are imported, we `tidy`:

```{r, tidy}
DL1202_tidied <- tidy(DL1202_utf8)
```

This function renames columns and does simple mutations, such as:

* Converts names to uppercase
* Moves suffixes from first or last name columns to the appropriate suffix column
* Removes punctuation from middle initial column
* Removes ending hyphen from zip codes with only 5 digits

### proof

After data are tidied, we `proof`:

```{r, proof}
DL1202_proofed <- proof(DL1202_tidied, year = 2020)
```

Data that are considered irregular are flagged in a new column called "errors". No actual corrections take place in this step; all data remain identical except for the new "errors" column. For each field, values are compared to standard expected formats and if they do not conform, the field name is pasted as a string in the "errors" column. Each row can have from zero errors (NA) to all column names listed. Multiple flags are hyphen delimited. 

The year of the Harvest Information Program must be supplied as a parameter. This aids in checking dates when licenses were issued, as one example.

## Stage 2: Visualize Data

### errorPlot_fields

The `errorPlot_fields` function can be run on all states, provinces, and/or territories in the data...

```{r errorfieldsplotall, fig.width = 6}
errorPlot_fields(DL1202_proofed, loc = "all")
```

... or it can be limited to just one.

```{r errorfieldsplotsc, fig.width = 6}
errorPlot_fields(DL1202_proofed, loc = "SC")
```

The year can also be specified in `errorPlot_fields` to visualize the proportion of "errors" created by youth hunters, since their birth dates fall outside the expected parameters of the `proof` function.

```{r errorfieldsplotyouth, fig.width = 6}
errorPlot_fields(DL1202_proofed, loc = "SC", year = 2020)
```


### errorPlot_states

The `errorPlot_states` function can plot errors as either proportions or counts by state. 

```{r errorstatesprop, fig.width = 6}
errorPlot_states(DL1202_proofed, type = "proportion")
```

```{r errorstatescount, fig.width = 6}
errorPlot_states(DL1202_proofed, type = "count")
```

### findDuplicates

The `findDuplicates` function ... (in progress)

```{r findDuplicates, fig.width = 6}
findDuplicates(DL1202_proofed)
```

### outOfStateHunters

The `outOfStateHunters` function allows us to visualize how many hunters report harvests from a location that does not match the state, province, or territory of their address. A list is returned from this function, so a table can be written to .csv from the first list element if needed.

```{r outofstate, fig.width = 6}
outOfStateHunters(DL1202_proofed)
```

### youthHunters

The `youthHunters` function returns a listed table and plot of the number of hunters with birth dates < 16 years from the year of HIP data collection. These data are interesting to explore because hunters younger than 16 years of age are not required to have a migratory bird hunting license in the United States. 

```{r youth, fig.width = 6}
youthHunters(DL1202_proofed, year = 2020)
```

## Stage 3: Explore Errors

### errorTable

The `errorTable` function is a flexible way to obtain error data as a tibble, which can be assessed as needed or exported to create records of download cycle errors. The basic function reports errors by both location and field.

```{r errortable1}
errorTable(DL1202_proofed)
```

Errors can be reported by only location by turning off the `field` parameter.

```{r errortable2}
errorTable(DL1202_proofed, field = "none")
```

Errors can be reported by only field by turning off the `loc` parameter.

```{r errortable3}
errorTable(DL1202_proofed, loc = "none")
```

Location can be specified.

```{r errortable4}
errorTable(DL1202_proofed, loc = "CA")
```

Field can be specified.

```{r errortable5}
errorTable(DL1202_proofed, field = "suffix")
```

Total errors for a location can be pulled.

```{r errortable6}
errorTable(DL1202_proofed, loc = "CA", field = "none")
```

Total errors for a field in a particular location can be pulled.

```{r errortable7}
errorTable(DL1202_proofed, loc = "CA", field = "zip")
```

### pullErrors

The `pullErrors` function can be used to view all of the actual values that were flagged as errors in a particular field. In this example, we find that the "dove_bag" field contains entries of "4" and "9", when the only values permissible are 0, 1, 2, 3, and 5.

```{r pullerrors}
pullErrors(DL1202_proofed, error = "dove_bag")
```

### redFlags

<b>By state.</b>
States with an unacceptable level of error can be pulled into a tibble. The tibble contains information pertaining to state, the count of errors from that state, the number of correct records from that state, the proportion of error per state, and a "flag" column that prints the threshold used. Any threshold can be supplied; in this example, we see which states had more than 3% error.

```{r redflags1}
redFlags(DL1202_proofed, type = "state", threshold = 0.03)
```

<b>By field.</b>
The same can be done for data fields. In this example, we see which fields had more than 1% error.

```{r redflags2}
redFlags(DL1202_proofed, type = "field", threshold = 0.01)
```

## Stage 4: Correct and Compare

### correct

After the download data are proofed, the next step is to fix the data to the best of our ability. Data can be corrected by running the `correct` function on the proofed tibble.

The year of the Harvest Information Program must be supplied as a parameter. Since the "errors" column is re-created using `correct`, supplying the year is necessary for the same reasons it is required by `proof`. 

```{r correct}
DL1202_corrected <- correct(DL1202_proofed, year = 2020)
```

If errors remain after running automated corrections, they may be corrected semi-manually. This feature is in progress.

All functions in <b>Stage 2</b> and <b>Stage 3</b> will run on the corrected tibble, DL1202_corrected, just as they worked on the example tibble DL1202_proofed. Errors can be compared between the proofed stage and corrected stage to get a better idea of which errors were serious (i.e., difficult to correct automatically) and determine how serious errors can be prevented in the future.

## Troubleshooting

<b>Questions?</b> Contact Abby Walter, abby_walter@fws.gov

