---
title: "The migbirdHIP Workflow"
output:
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The migbirdHIP Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Table of Contents

-   [Introduction](#introduction)
    -   [Installation](#installation)
        -   [Releases](#releases)
    -   [Load](#load)
    -   [Functions overview](#functions-overview)
-   [Part A: Data Import and Cleaning](#part-a-data-import-and-cleaning)
    -   [fileRename](#filerename)
    -   [fileCheck](#filecheck)
    -   [read_hip](#read_hip)
    -   [glyphCheck](#glyphcheck)
    -   [shiftCheck](#shiftcheck)
    -   [clean](#clean)
    -   [issueCheck](#issuecheck)
    -   [duplicateFinder](#duplicatefinder)
    -   [duplicateFix](#duplicatefix)
    -   [bagCheck](#bagcheck)
    -   [proof](#proof)
    -   [correct](#correct)
-   [Part B: Data Visualization and Tabulation](#part-b-data-visualization-and-tabulation)
    -   Visualization
        -   [duplicatePlot](#duplicateplot)
        -   [errorPlotFields](#errorplotfields)
        -   [errorPlotStates](#errorplotstates)
        -   [errorPlotDL](#errorplotdl)
    -   Tabulation
        -   [pullErrors](#pullerrors)
        -   [errorTable](#errortable)
-   [Part C: Writing Data and Reports](#part-c-writing-data-and-reports)
    -   [write_hip](#write_hip)
    -   [writeReport](#writereport)

## Introduction {#introduction}

The `migbirdHIP` package was created by the U.S. Fish and Wildlife Service (USFWS) to process, clean, and visualize Harvest Information Program (HIP) registration data.

Every year, migratory game bird hunters must register for HIP in the state(s) they plan to hunt by providing their name, address, date of birth, and hunting success from the previous year. All 49 contiguous states are responsible for collecting this information and submitting hunter registrations to the USFWS. Raw data submitted by the states are processed in this package.

The USFWS has been using HIP registrations since 1999 to select hunters for the Migratory Bird Harvest Survey (Diary Survey) and the Parts Collection Survey (Wing Survey). Only a small proportion of HIP registrants are chosen to complete these surveys each year. The USFWS ultimately uses these data to generate annual harvest estimates. To read more about HIP and the surveys, visit: <https://www.fws.gov/harvestsurvey/> and <https://www.fws.gov/library/collections/migratory-bird-hunting-activity-and-harvest-reports>

### Installation {#installation}

The package can be installed from the USFWS GitHub repository using:

```{r, install, eval = FALSE}
devtools::install_github(
  "USFWS/migbirdHIP",
  quiet = T,
  upgrade = F,
  build_vignettes = T
)
```

#### Releases {#releases}

To install a past release, use the example below and substitute the appropriate version number. Releases are documented in the [README](https://github.com/USFWS/migbirdHIP/blob/main/README.md#releases).

```{r, releases, eval = FALSE}
devtools::install_github("USFWS/migbirdHIP@v1.2.8", build_vignettes = T)
```

### Load {#load}

Load `migbirdHIP` after installation. The package will return a startup message with the version you have installed and what season of HIP data the package version was intended for.

```{r setup}
library(migbirdHIP)
```

### Functions overview {#functions-overview}

The flowchart below is a visual guide to the order in which functions are used. Some functions are only used situationally and some issues with the data cannot be solved using a function at all. The general process of handling HIP data is demonstrated in the flowchart; every exported function in the `migbirdHIP` package is included in it and the vignette.

```{r flowchart_svg, echo = FALSE, fig.cap = "Overview of migbirdHIP functions in a flowchart format.", out.width = "100%", dev = "svg", fig.align = "center"}
knitr::include_graphics(
  paste0(here::here(), "/man/figures/migbirdHIP_flowchart.svg"))
```

## Part A: Data Import and Cleaning {#part-a-data-import-and-cleaning}

### fileRename {#filerename}

The `fileRename()` function renames non-standard file names to the standard format. We expect a file name to be a 2-letter capitalized state abbreviation followed by YYYYMMDD (indicating the date data were submitted).

Some states submit files using a 5-digit file name format, containing 2 letters for the state abbreviation followed by a 3-digit Julian date. To convert these 5-digit filenames to the standard format (a requirement to read data properly with [read_hip()](#read_hip)), supply `fileRename()` with the directory containing HIP data. File names will be automatically overwritten with the YYYYMMDD format date corresponding to the submitted Julian date.

This function also converts lowercase state abbreviations to uppercase.

The current hunting season year must be supplied to the `year` parameter to accurately convert dates.

```{r rename, eval = FALSE}
fileRename(path = "C:/HIP/raw_data/DL0901", year = 2024)
```

### fileCheck {#filecheck}

Check if any files in the input folder have already been written to the processed folder using `fileCheck()`.

```{r filecheck, eval = FALSE}
fileCheck(
  raw_path = "C:/HIP/raw_data/DL0901/",
  processed_path = "C:/HIP/corrected_data/"
)
```

### read_hip {#read_hip}

Read HIP data from fixed-width `.txt` files using `read_hip()`. Files must adhere to a 10-character naming convention to successfully be read in (2-letter capitalized state abbreviation followed by `YYYYMMDD`); if files were submitted with a 5-digit format or lowercase state abbreviation, run [fileRename](#filerename) first.

**Note:** In the `read_hip()` example below, we use an internal directory to read in fake HIP data files, which allows the function to demonstrate its errors and messages. (The testing data were generated with `data-raw/create_fake_HIP_data.R` and are stored under `inst/extdata/`.) All other examples in this vignette will use `C:/` drive examples for clarity.

```{r, readhip}
raw_data <- read_hip(paste0(here::here(), "/inst/extdata/DL0901/"))
```

#### The `read_hip()` function allows data to be read in for:

-   all states (e.g., `state = NA`, the default)
-   a specific state (e.g., `state = "DE"`)
-   a specific download (e.g., `season = FALSE`, the default; `path` must be to the download's subdirectory)
-   an entire season (e.g., `season = TRUE`, and `path` is to the directory containing all download subdirectories)

Use `unique = TRUE` to read in a frame without exact duplicates, or `unique = FALSE` to read in all registrations including exact duplicates.

Data are read in an expected format beginning with the `title` field and ending with `email` field. Additional fields are created by `read_hip()`: `dl_state`, `dl_date`, `source_file`, `dl_cycle`, `dl_key`, `record_key`.

#### The `read_hip()` function returns a message if:

-   There is a `dl_state` not found in the list of 49 continental US states
-   `MMDDYYYY` or `DDMMYYYY` format suspected in `dl_date`
-   Blank files are found in the directory
-   `NA` values detected in one or more ID fields (`firstname`, `lastname`, `state`, `birth_date`) for \>10% of a file and/or \>100 registrations
-   All emails are missing from a file
-   Test records are found
-   Any registration has a `0` in every bag field
-   Any registration has an `NA` in every bag field
-   Any registration contains a bag value that is not a 1-digit number
-   There is an `NA` in `dl_state`
-   There is an `NA` in `dl_date`
-   For presumed solo permit DNHs; if any OR or WA `hunt_mig_birds` does not equal `2` when non-permit bags are `0` and one of `band_tailed_pigeon`, `brant`, and/or `seaduck` is `2`.

As an example, we will use the default `read_hip()` settings to read in all of the states from download 0901, using fake HIP data files located in the `extdata/DL0901/` directory of the R package.

### glyphCheck {#glyphcheck}

During pre-processing, R may throw an error that says something like "invalid UTF-8 byte sequence detected". The error usually includes a field name but no other helpful information. The `glyphCheck()` function identifies values containing non-UTF-8 glyphs/characters and prints them with the source file in the console so they can be edited.

```{r glyphCheck}
glyphCheck(raw_data)
```

### shiftCheck {#shiftcheck}

Find and print any rows that have a line shift error with `shiftCheck()`.

```{r shiftCheck}
shiftCheck(raw_data)
```

### clean {#clean}

The `clean()` function performs data cleaning and filters out bad registrations.

```{r, clean}
clean_data <- clean(raw_data)
```

#### Registrations are dropped if:

-   Any bag value is not a 1-digit number.
-   `NA` or `0` for every bag field
-   Test record is detected
-   One of:
    -   `firstname`, `lastname`, `state`, or `birth_date` is `NA`
    -   `address` AND `email` are `NA`, `city`
    -   AND/OR `zip` AND `email` are `NA`

#### Changes include:

-   `firstname`
    -   Change to uppercase
    -   If a suffix value is detected (e.g. JR, SR, 1ST-20TH and 1-20 in Roman numerals, excluding XVIII) delete it. Delete white space around string.
-   `lastname`
    -   Change to uppercase
    -   If a suffix value is detected (e.g. JR, SR, 1ST-20TH and 1-20 in Roman numerals, excluding XVIII) delete it. Delete white space around string.
-   `suffix`
    -   Change to uppercase
    -   If a suffix value is detected in firstname or lastname, replace the suffix field with that value. Values that are searched for include JR, SR, 1ST-20TH and 1-20 in Roman numerals, excluding XVIII. Periods and commas are deleted.
-   `zip`
    -   Remove ending hyphen from zip codes with only 5 digits
    -   Remove ending 0 from zip codes with 10 digits
    -   Insert a hyphen in continuous 9 digit zip codes
    -   Insert a hyphen in 9 digit zip codes with a middle space
    -   Delete trailing -0000 and -\_\_\_\_
-   `hunt_mig_birds`
    -   For Oregon and/or Washington, if `HuntY` is `0` and if `band_tailed_pigeon`, `brant`, or `seaduck` is `2`, change `hunt_mig_birds` field from `0` to `2`
-   `band_tailed_pigeon`
    -   If any permit file states submitted a `2` for crane, change the `2` to a `0`
-   `cranes`
    -   If any permit file states submitted a `2` for band_tailed_pigeon, change the `2` to a `0`

In addition to the changes listed above, the internal `zipCheck()` function returns a message from `clean()` if zip codes are detected that do not correspond to provided state of residence for \>10% of a file and/or \>100 registrations.

### issueCheck {#issuecheck}

The `issueCheck()` function assesses the validity of the `issue_date` field based on the current hunting season's HIP issuance start and end dates (not season open and close dates) for every state except Mississippi. A plot is automatically returned for past and future registrations; to skip plotting, specify `plot = F`.

```{r, issuecheck, eval = F}
current_data <- issueCheck(clean_data, year = 2024, plot = F)
```

```{r, createcurrent, include = F}
current_data <- clean_data
```

#### Criteria evaluated and changes made:

- **Current record:** a record's `issue_date` falls between the start and end dates of HIP issuance for its state; if not already, change `registration_yr` to current season.
- **Past record:** a record's `issue_date` is before the start date of HIP issuance for its state; these records are filtered out.
- **Future record:** a record has an `issue_date` after the last day of hunting for its state; the `registration_yr` is changed to `registration_yr + 1`.
- **Bad `issue_date`:** a record's `issue_date` cannot be evaluated, likely because it's formatted incorrectly or equals `"00/00/0000"`; these records are filtered out.
- Return message if any record's `issue_date` is after the file was submitted.

### duplicateFinder {#duplicatefinder}

The `duplicateFinder()` function finds hunters that have more than one registration. Registrations are grouped by `firstname`, `lastname`, `state`, `birth_date`, `dl_state`, and `registration_yr` to identify unique hunters. If the same hunter has 2 or more registrations, the fields that are not identical are counted and summarized.

Plot the duplicates with [duplicatePlot](#duplicateplot).

```{r findDuplicates_tbl}
duplicateFinder(current_data)
```

### duplicateFix {#duplicatefix}

We sometimes receive multiple HIP registrations per person which must be resolved by `duplicateFix()`. Duplicates are identified when more than one registration has the same `firstname`, `lastname`, `state`, `birth_date`, `dl_state`, and `registration_yr`. Only 1 HIP registration per hunter can be kept. For in-line permit states (`r unique(migbirdHIP:::REF_PMT_INLINE$dl_state)`), permit records are submitted separately from HIP registrations. Multiple permits are allowed. We differentiate `HIP` and `PMT` records from in-line permit states, we check the values in the non-permit species fields (`ducks_bag`, `geese_bag`, `dove_bag`, `woodcock_bag`, `coots_snipe`, `rails_gallinules`). HIP registrations contain non-zero values in those columns, but permit records always have `0` values.

```{r, duplicateFix}
deduplicated_data <- duplicateFix(current_data)
```

To decide which HIP registration to keep from a group, we follow a series of logic.

#### For sea duck and brant states:

These states include: `r paste0(migbirdHIP:::REF_STATES_SD_BR, collapse = ", ")`

1.  Keep registration(s) with the most recent issue date.
2.  Exclude registrations with all 1s or all 0s in bag columns from consideration.
3.  Keep any registrations that have a 2 for either brant or sea duck (for seaduck and brant states), or 2 for seaduck (Maine only).
4.  If more than one registration remains, choose to keep one randomly.

#### For HIP registrations from in-line permit states and all other states:

These states include: `r paste0(migbirdHIP:::REF_ABBR_49_STATES[!migbirdHIP:::REF_ABBR_49_STATES %in% c(migbirdHIP:::REF_STATES_SD_BR, migbirdHIP:::REF_STATES_SD_ONLY)], collapse = ", ")`

1.  Keep registration(s) with the most recent issue date.
2.  Exclude registrations with all 1s or all 0s in bag columns from consideration, if possible.
3.  If more than one registration remains, choose to keep one randomly.

A new field called `record_type` is added to the data after the above deduplicating process. Every HIP registration is labeled `HIP`. In-line permit states WA and OR send HIP and permit records separately, which are labeled `HIP` and `PMT` respectively.

### bagCheck {#bagcheck}

Running `bagCheck()` ensures species "bag" values are in order. This function searches for values in species group columns that are not typical or expected by the US Fish and Wildlife Service. If a value outside of the normal range is detected, an output tibble is created. Each row in the output contains the state, species, unusual stratum value, and a list of the normal values we would expect.

If a value for a species group is given in the HIP data that doesn't match anything in our records, the species reported in the output will have `NA` values in the `normal_strata` column. These species are not hunted in the reported states.

```{r, bagCheck}
bagCheck(deduplicated_data)
```

### proof {#proof}

After data are cleaned and checked in the steps above, we run `proof()` to check for errors. Note that no actual corrections or data changes take place as a result of this function. The year of the Harvest Information Program must be supplied to the `year` parameter, which aids in checking `registration_yr`, `issue_date` and `birth_date`.

Values that are considered irregular are flagged in a new field called `errors`. For each existing field (`r paste(migbirdHIP:::REF_FIELDS_ALL, collapse = ", ")`), values are compared to standard expected formats. If they do not conform, the field name is pasted as a string in the `errors` column. Each row can have anywhere from zero errors (`NA`) to all field names listed. Multiple errors per registration are hyphen delimited. A typical `errors` value would look like: `"suffix-address-zip"`, `"zip"`, or `"middle-email"`.

```{r, proof}
proofed_data <- proof(deduplicated_data, year = 2024)
```

#### What gets flagged in the `errors` field and why:

-   `"test_record"`
    -   `firstname` and `lastname` are `"TEST"`
    -   `lastname` is `"INAUDIBLE"`
    -   `firstname` is one of: `"INAUDIBLE", "BLANK", "USER", "TEST", "RESIDENT"`
-   `"title"` if `title` is not one of: `NA`, `0`, `1` or `2`.
-   `"firstname"`
    -   `firstname` contains anything other than letters, apostrophe(s), space(s), and/or hyphen(s)
    -   `firstname` contains less than 2 letters
    -   `firstname` contains `"AKA"`
-   `"middle"` if `middle` is not exactly 1 letter or `NA`
-   `"lastname"`
    -   `lastname` contains anything except letters, apostrophe(s), space(s), hyphen(s), and/or period(s)
    -   `lastname` contains less than 2 letters
-   `"suffix"`
    -   `suffix` should be one of: `I, II, III, IV, V, VI, VII, VIII, IX, X, XI, XII, XIII, XIV, XV, XVI, XVII, XIX, XX, 1ST, 2ND, 3RD, 4TH, 5TH, 6TH, 7TH, 8TH, 9TH, 10TH, 11TH, 12TH, 13TH, 14TH, 15TH, 16TH, 17TH, 18TH, 19TH, 20TH, JR, SR`.
    -   Note that `XVIII` is excluded (exceeds 4 character limit)
-   `"address"` if `address` contains a `|`, tab, or non-UTF8 character
-   `"city"`
    -   `city` contains anything other than letters, space(s), hyphen(s), apostrophe(s), and/or period(s)
    -   `city` contains less than 3 letters
-   `"state"` if `state` is not contained in the following list of abbreviations for US states and territories and Canadian provinces and territories:
    -   `r paste0(c(migbirdHIP:::REF_ABBR_49_STATES, migbirdHIP:::REF_ABBR_USA, migbirdHIP:::REF_ABBR_CANADA), collapse = ", ")`
-   `"zip"`
    -   If a registration's `address` doesn't have a `zip` that should be in their reported address `state` of residence
-   `"birth_date"` if the year in `birth_date` is more than `100` or less than `0` years ago
-   `"hunt_mig_birds"` if not equal to `1` or `2`
-   `"registration_yr"` if not equal to the HIP data collection year
-   `"email"`
    -   `email` does not match universally accepted email regex (see `REGEX_EMAIL`)
    -   `email` is obfuscative
        -   e.g., ``` none@gmail.com, nottoday@gmail.co``m, fake.fake@gmail.com``, n@a.com, x@y.com, brian@na.com ```, etc (see `REGEX_EMAIL_OBFUSCATIVE_LOCALPART`, `REGEX_EMAIL_OBFUSCATIVE_DOMAIN`, and `REGEX_EMAIL_OBFUSCATIVE_ADDRESS`)
        -   A repeated character is detected, e.g. `aaa@a.com` (see `REGEX_EMAIL_REPEATED_CHAR`)
        -   The domain is `tpwd.texas.gov` or some variation (see `REGEX_EMAIL_OBFUSCATIVE_TPWD`)
        -   A `walmart.com` domain is preceded by only numbers (see `REGEX_EMAIL_OBFUSCATIVE_WALMART`)
    -   `email` is longer than 100 characters
    -   A common domain name (e.g., gmail, yahoo) has a common typo
    -   A common domain name doesn't have a matching top-level domain (e.g., `gmail.net` or `hotmail.gov`)
    -   The address has a bad top-level domain (e.g., `.comcom`, `.ccom`, etc.)
    -   The email is missing a top-level domain
    -   The top-level domain period is missing (e.g., `gmailcom`).

### correct {#correct}

Data can be corrected by running the `correct()` function with year of the Harvest Information Program supplied to the `year` parameter.

```{r correct}
corrected_data <- correct(proofed_data, year = 2024)
```

#### Changes and corrections include:

-   `title` is changed to `NA` if `"title"` is in the `errors` field

-   `middle` is changed to `NA` if `"middle"` is in the `errors` field

-   `suffix` is changed to `NA` if `"suffix"` is in the `errors` field

-   `email`

    -   Add endings to common domains if missing (e.g. `@gmail` would become `@gmail.com`), for domains including:
        -   `gmail, yahoo, hotmail, aol, icloud, comcast, outlook, sbcglobal, att, msn, live, bellsouth, charter, ymail, me, verizon, cox, earthlink, protonmail, pm, mail, duck, ducks`
    -   Add top-level domain period(s) if:
        -   Missing before `com, net, edu, gov, org`
        -   Missing in `navymil, mailmil, armymil; add multiple periods if missing to usnavymil, usafmil, usarmymil, usacearmymil`

-   `errors` is updated by re-running `proof()` inside of `correct()`


## Part B: Data Visualization and Tabulation {#part-b-data-visualization-and-tabulation}

### duplicatePlot {#duplicateplot}

Plot duplicates with `duplicatePlot()`.

```{r, duplicatePlot, fig.cap = "Figure 1. Plot of types of duplicates.", fig.width = 6, fig.height = 3.5, dpi = 300, out.width = 500, fig.align = "center"}
duplicatePlot(current_data)
```

### errorPlotFields {#errorplotfields}

The `errorPlotFields()` function can be run on all states...

```{r errorfieldsplotall, fig.cap = "Figure 2. Plot of all location's errors by field name.", fig.width = 6, fig.height = 3.6, dpi = 300, out.width = 500, fig.align = "center"}
errorPlotFields(proofed_data, loc = "all", year = 2024)
```

... or it can be limited to just one.

```{r errorfieldsplotsc, fig.cap = "Figure 3. Plot of Louisiana's errors by field name.", fig.width = 6, fig.height = 3.6, dpi = 300, out.width = 500, fig.align = "center"}
errorPlotFields(proofed_data, loc = "LA", year = 2024)
```

It is possible to add any `ggplot2` components to these plots. A plot can be altered with `facet_wrap` using either `dl_cycle` or `dl_date`. The example below demonstrates how this package's functions can interact with `tidyverse` and shows an example of an `errorPlotFields` with `facet_wrap` (using a subset of 4 download cycles).

```{r errorfieldsfacet, eval = FALSE}
errorPlotFields(
  hipdata2024 |>
    filter(str_detect(dl_cycle, "0800|0901|0902|1001")),
    year = 2024) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0, hjust = 1),
    legend.position = "bottom") +
  facet_wrap(~dl_cycle, ncol = 2)
```

### errorPlotStates {#errorplotstates}

The `errorPlotStates()` function plots error proportions per state. A threshold value must be set to only view states above a certain proportion of error (in the example below, `threshold = 0.05` indicates an error tolerance of 5%). Bar labels are error counts.

```{r errorplotstates, fig.cap = "Figure 5. Plot of proportion of error by state.", fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center"}
errorPlotStates(proofed_data, threshold = 0.05)
```

### errorPlotDL {#errorplotdl}

This function should not be used unless you want to visualize an entire season of data. The `errorPlotDL()` function plots proportion of error per download cycle over the course of the hunting season. Location may be specified with the `loc` parameter to see a particular state over time.

```{r errorPlotDL, eval = FALSE}
errorPlotDL(hipdata2024, loc = "MI")
```

```{r errorplotdl_example, echo = FALSE, fig.cap = "errorPlot_dl example output", out.width = "70%", fig.align = "center"}
knitr::include_graphics(paste0(here::here(), "/man/figures/errorPlot_dl.png"))
```

### pullErrors {#pullerrors}

The `pullErrors()` function can be used to view all of the actual values that were flagged as errors in a particular field. In this example, we find that the `suffix` field contains several values that are not accepted.

```{r pullerrors}
pullErrors(proofed_data, field = "suffix")
```

Running `pullErrors()` on a field that has no errors will return a message.

```{r pullerrors2}
pullErrors(proofed_data, field = "dove_bag")
```

### errorTable {#errortable}

The `errorTable()` function returns error data as a tibble, which can be assessed as needed or exported to create records of download cycle errors. The basic function reports errors by both location and field.

```{r errortable1}
errorTable(proofed_data)
```

Errors can be reported by only location by turning off the `field` parameter.

```{r errortable2}
errorTable(proofed_data, field = "none")
```

Errors can be reported by only field by turning off the `loc` parameter.

```{r errortable3}
errorTable(proofed_data, loc = "none")
```

Location can be specified using one of the 49 contiguous state abbreviations.

```{r errortable4}
errorTable(proofed_data, loc = "CA")
```

Field can be specified (one of: `r paste(c("all", "none", migbirdHIP:::REF_FIELDS_ALL), collapse = ", ")`).

```{r errortable5}
errorTable(proofed_data, field = "suffix")
```

Total errors for a location can be pulled.

```{r errortable6}
errorTable(proofed_data, loc = "CA", field = "none")
```

Total errors for a field in a particular location can be pulled.

```{r errortable7}
errorTable(proofed_data, loc = "CA", field = "dove_bag")
```

## Part C: Writing Data and Reports {#part-c-writing-data-and-reports}

### write_hip {#write_hip}

After the data have been corrected, the data are ready to be written out. Use `write_hip()` to do final processing to the data, which includes 1) adding in FWS strata and 2) setting `NA` values to blank strings. If `split = FALSE`, the final table will be saved as a single `.csv` to your specified path. If `split = TRUE` (default), one `.csv` file per each input `.txt` source file will be written to the specified directory.

```{r, writecsv, eval = FALSE}

write_hip(corrected_data, path = "C:/HIP/processed_data/")

```

### writeReport {#writereport}

The `writeReport()` function can be used to automatically generate an R markdown document with figures, tables, and summary statistics. This can be done at the end of a download cycle.

```{r, writerpt, eval = FALSE}

writeReport(
  raw_path = "C:/HIP/DL0901/",
  temp_path = "C:/HIP/corrected_data",
  year = 2024,
  dl = "0901",
  dir = "C:/HIP/dl_reports",
  file = "DL0901_report")
```
