---
title: "Harvest Information Program Download Cycle Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: cerulean
params:
  comp_path:
    value: x
  year:
    value: x
---

```{r libs, include = FALSE}
library(tidyverse)
```

```{r import, include = FALSE}

dl_data <- compile_to_utf8(params$comp_path)

tidied_data <- tidy(dl_data)

proofed_data <- proof(tidied_data, year = params$year)

# Remove original and tidied data to improve memory use
rm(dl_data)
rm(tidied_data)

corrected_data <- correct(proofed_data, year = params$year)

```

# Introduction

This is a report of download cycle `r proofed_data %>% select(dl_cycle) %>% distinct %>% pull`. This cycle, **`r nrow(proofed_data)`** records were submitted from **`r proofed_data %>% select(dl_state) %>% distinct %>% nrow()`** states.

# Visualization of errors

To get a general idea of what the data look like, first we visualize the errors as plots.

## Error plots

### Errors by field

**Before correction**

```{r erpf, echo = FALSE}
errorPlot_fields(proofed_data, specify = params$year)
```

**After correction**

```{r erpf_c, echo = FALSE}
errorPlot_fields(corrected_data, specify = params$year)
```

### Errors by state

**Before correction**

```{r erps, echo = FALSE}
errorPlot_states(proofed_data, type = "proportion")
```

**After correction**

```{r erps_c, echo = FALSE}
errorPlot_states(corrected_data, type = "proportion")
```

## Duplicates

```{r fd, echo = FALSE}
findDuplicates(proofed_data)
```

## Out-of-state hunters

```{r oosh_c, echo = FALSE}
outOfStateHunters(corrected_data, type = "proportion")
```

## Youth hunters

```{r yh, echo = FALSE}
youthHunters(proofed_data, year = params$year)
```

# Explore errors

Let's take a closer look at common errors and issues within this download's HIP data.

## High error counts

**Q: What were the most common errors, and what values caused them?**

Tibble of most common errors...

```{r et, echo = FALSE}
et <- errorTable(proofed_data, loc = "none") %>% arrange(desc(error_count))

et
```

Values associated with error in **`r et$error[1]`**

```{r pe_1, echo = FALSE}
err1 <- pullErrors(proofed_data, error = et$error[1])

if(length(err1) > 20){
  err1[1:20]
  } else {
  err1
    }
```

Values associated with error in **`r et$error[2]`**

```{r pe_2, echo = FALSE}
err2 <- pullErrors(proofed_data, error = et$error[2])

if(length(err2) > 20){
  err2[1:20]
  } else {
  err2
    }
```

Values associated with error in **`r et$error[3]`**

```{r pe_3, echo = FALSE}
err3 <- pullErrors(proofed_data, error = et$error[3])

if(length(err3) > 20){
  err3[1:20]
  } else {
  err3
    } 
```

## High error proportions

**Q: What states and fields had a proportion of error that exceeded an acceptable threshold?**

**States** with more than 1% error

```{r rfs, echo = FALSE}
redFlags(proofed_data, type = "state", threshold = 0.1)
```

**Fields** with more than 1% error

```{r rff, echo = FALSE}
redFlags(proofed_data, type = "field", threshold = 0.1)
```
