---
title: "Harvest Information Program Download Cycle Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: cerulean
params:
  comp_path:
    value: x
  year:
    value: x
---

```{r import, include = FALSE}

dl_data <- compile_to_utf8(params$comp_path)

tidied_data <- tidy(dl_data)

proofed_data <- proof(tidied_data, year = params$year)

# Remove original and tidied data to improve memory use
rm(dl_data)
rm(tidied_data)

corrected_data <- correct(proofed_data, year = params$year)

```

# Introduction

This is a report of download cycle `r proofed_data$dl_cycle %>% distinct %>% pull`. This cycle, `r nrow(proofed_data)` records were submitted from `r proofed_data %>% select(dl_state) %>% distinct %>% nrow()` states.

# Visualization of errors

## Error plots

### Errors by field

**Before correction**
```{r erpf, echo = FALSE}
errorPlot_fields(proofed_data, specify = params$year)
```

**After correction**
```{r erpf_c, echo = FALSE}
errorPlot_fields(corrected_data, specify = params$year)
```

### Errors by state

**Before correction**
```{r erps, echo = FALSE}
errorPlot_states(proofed_data, type = "proportion")
```

**After correction**
```{r erps_c, echo = FALSE}
errorPlot_states(corrected_data, type = "proportion")
```

## Duplicates

**Before correction**
```{r fd, echo = FALSE}
findDuplicates(proofed_data)
```

**After correction**
```{r fd_c, echo = FALSE}
findDuplicates(corrected_data)
```

## Out-of-state hunters

```{r oosh_c, echo = FALSE}
outOfStateHunters(corrected_data, type = "proportion")
```

## Youth hunters

```{r yh, echo = FALSE}
youthHunters(proofed_data, year = params$year)
```

# Explore errors

## errorTable

```{r et, echo = FALSE}
library(tidyverse)

et <- errorTable(proofed_data, loc = "none") %>% arrange(desc(error_count))

et
```

## pullErrors

```{r pe, echo = FALSE}
pullErrors(proofed_data, error = et$error[1])

pullErrors(proofed_data, error = et$error[2])

pullErrors(proofed_data, error = et$error[3])
```

## redFlags

```{r rf, echo = FALSE}
redFlags(proofed_data, type = "state", threshold = 0.5)

redFlags(proofed_data, type = "field", threshold = 0.5)
```
