---
title: "Harvest Information Program Download Cycle Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: cerulean
params:
  comp_path:
    value: x
  year:
    value: x
---

```{r import, include = FALSE}

season_data <- compile_to_utf8(params$comp_path)

tidy_data <- tidy(season_data)

proofed_data <- proof(tidied_data, year = params$year)

corrected_data <- correct(proofed_data, year = params$year)

```

# Introduction

This is a report of download cycle `proofed_data$dl_cycle %>% distinct %>% pull`.

# Visualization of errors

## Error plots

### Errors by field

#### Before correction
```{r erpf, echo = FALSE}
errorPlot_fields(proofed_data, specify = params$year)
```

#### After correction
```{r erpf_c, echo = FALSE}
errorPlot_fields(corrected_data, specify = params$year)
```

### Errors by state

#### Before correction
```{r erps, echo = FALSE}
errorPlot_states(proofed_data, type = "proportion")
```

#### After correction
```{r erps_c, echo = FALSE}
errorPlot_states(corrected_data, type = "proportion")
```

## Duplicates

#### Before correction
```{r fd, echo = FALSE}
findDuplicates(proofed_data)
```

### After correction
```{r fd_c, echo = FALSE}
findDuplicates(corrected_data)
```

## Out-of-state hunters

### Before correction
```{r oosh, echo = FALSE}
outOfStateHunters(proofed_data, type = "proportion")
```

### After correction
```{r oosh_c, echo = FALSE}
outOfStateHunters(corrected_data, type = "proportion")
```

## Youth hunters

```{r yh, echo = FALSE}
youthHunters(proofed_data, type = "proportion")
```

# Explore errors

## investigate


## errorTable


## pullErrors


## redFlags

