---
title: "Harvest Information Program Season Summary Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: cerulean
params:
  comp_path:
    value: x
  year:
    value: x
---

```{r libs, include = FALSE}
library(tidyverse)
library(DT)
library(shiny)
```

```{r import, include = FALSE}

season_data <- read_hip(params$comp_path)

cleaned_data <- clean(season_data)

# Remove original data to improve memory use
rm(season_data)

fixed_data <- fixDuplicates(cleaned_data)

proofed_data <- proof(fixed_data, year = params$year)

corrected_data <- correct(proofed_data, year = params$year, data = "bag")

```

# Introduction

This is a summary report of the `r params$year` Season of Harvest Information Program (HIP) data. This year, `r nrow(fixed_data)` unique records were submitted in `r length(list.files(params$comp_path, recursive = TRUE) %>% as_tibble() %>% transmute(filepath = as.character(value)) %>% mutate(filepath = str_replace(filepath, "TXT", "txt")) %>% filter(str_detect(filepath, "(?<=\\.)txt$")) %>% pull)` files from `r proofed_data %>% select(dl_state) %>% distinct %>% nrow()` states.

Below is a table summarizing the total of number of records per download state.

```{r sum_per_state, echo = FALSE, message = FALSE}

DT::datatable(cleaned_data %>% 
                select(dl_state) %>% 
                group_by(dl_state) %>% 
                summarize(sum = n()) %>% 
                ungroup())

```

# Data Checking

## Unique issue dates

```{r issuedates, echo = FALSE}
DT::datatable(cleaned_data %>% 
                select(issue_date, dl_state) %>% 
                distinct())
```

## Duplicates

### Before fixDuplicates (all 49 states)

```{r b_fd, echo = FALSE}
findDuplicates(cleaned_data)

DT::datatable(findDuplicates(cleaned_data, return = "table"))
```

### After fixDuplicates (all 49 states)

```{r a_fd, echo = FALSE}
findDuplicates(fixed_data)

DT::datatable(findDuplicates(fixed_data, return = "table"))
```

## Strata

```{r stratacheck, echo = FALSE}
DT::datatable(strataCheck(fixed_data))
```

## Repeated values

### Horizontal

```{r h_validate, echo = FALSE}
DT::datatable(migbirdHarvestData::validate(fixed_data, type = "horizontal"))
```

### Vertical

```{r v_validate, echo = FALSE}
DT::datatable(migbirdHarvestData::validate(fixed_data, type = "vertical"))
```

```{r data_sweep, include = FALSE}

# Remove data objects to improve memory use
rm(cleaned_data)
rm(fixed_data)
rm(perm_states)
```

# Error Visualizations

## By field

### Before correction

```{r erpf, echo = FALSE}
errorPlot_fields(proofed_data, year = params$year)
```

### After correction

```{r erpf_c, echo = FALSE}
errorPlot_fields(corrected_data, year = params$year)
```

## By state

### Before correction

```{r erps, echo = FALSE}
errorPlot_states(proofed_data)
```

### After correction

```{r erps_c, echo = FALSE}
errorPlot_states(corrected_data)
```

## By download

### Before correction

```{r erpdl, echo = FALSE}
errorPlot_dl(proofed_data)
```

### After correction

```{r erpdl_c, echo = FALSE}
errorPlot_dl(corrected_data)
```

## Out-of-state hunters

```{r oosh, echo = FALSE}
outOfStateHunters(proofed_data)
```

## Youth hunters

```{r yh, echo = FALSE}
youthHunters(proofed_data, year = params$year)
```

# Error Exploration

Let's take a closer look at common errors and issues within this season's HIP data.

## High error proportions

Q: What states and fields had a proportion of error that exceeded an acceptable threshold (before correction)?

States with more than 1% error

```{r rfs, echo = FALSE}
redFlags(proofed_data, type = "state", threshold = 0.1)
```

Fields with more than 1% error

```{r rff, echo = FALSE}
redFlags(proofed_data, type = "field", threshold = 0.1)
```
