---
title: "Harvest Information Program Season Summary Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: cerulean
params:
  comp_path:
    value: x
  year:
    value: x
---

```{r libs, include = FALSE}
library(tidyverse)
```

```{r import, include = FALSE}

season_data <- compile_to_utf8(params$comp_path)

tidied_data <- tidy(season_data)

proofed_data <- proof(tidied_data, year = params$year)

# Remove original and tidied data to improve memory use
rm(season_data)
rm(tidied_data)

corrected_data <- correct(proofed_data, year = params$year)

```

# Introduction

This is a summary report of the `r params$year` Season of Harvest Information Program (HIP) data. This year, `r nrow(proofed_data)` records were submitted from `r proofed_data %>% select(dl_state) %>% distinct %>% nrow()` states.

# Visualization of errors



## Error plots

### Errors by field

**Before correction**

```{r erpf, echo = FALSE}
errorPlot_fields(proofed_data, specify = params$year)
```

**After correction**

```{r erpf_c, echo = FALSE}
errorPlot_fields(corrected_data, specify = params$year)
```

### Errors by state

**Before correction**

```{r erps, echo = FALSE}
errorPlot_states(proofed_data, type = "proportion")
```

**After correction**

```{r erps_c, echo = FALSE}
errorPlot_states(corrected_data, type = "proportion")
```

### Errors by download

**Before correction**

```{r erpdl, echo = FALSE}
errorPlot_dl(proofed_data)
```

**After correction**

```{r erpdl_c, echo = FALSE}
errorPlot_dl(corrected_data)
```

## Duplicates

```{r fd_p, echo = FALSE}
findDuplicates(proofed_data)
```

## Out-of-state hunters

```{r oosh, echo = FALSE}
outOfStateHunters(proofed_data, type = "proportion")
```

## Youth hunters

```{r yh, echo = FALSE}
youthHunters(proofed_data, year = params$year)
```

# Explore errors

Let's take a closer look at common errors and issues within this season's HIP data.

## High error counts

**Q: What were the most common errors, and what values caused them?**

A: Tibble of most common errors...

```{r et, echo = FALSE}
et <- errorTable(proofed_data, loc = "none") %>% arrange(desc(error_count))
```

Values associated with error in `r et$error[1]`

```{r pe_1, echo = FALSE}
pullErrors(proofed_data, error = et$error[1])
```

Values associated with error in `r et$error[2]`

```{r pe_2, echo = FALSE}
pullErrors(proofed_data, error = et$error[2])
```

Values associated with error in `r et$error[3]`

```{r pe_3, echo = FALSE}
pullErrors(proofed_data, error = et$error[3])
```

## High error proportions

**Q: What states and fields had a proportion of error that exceeded a certain threshold?**

States that had more than 3% error in the data sent to the FIsh and Wildlife Service...

```{r rfs, echo = FALSE}
redFlags(proofed_data, type = "state", threshold = 0.3)
```

Fields that had more than 3% error...

```{r rff, echo = FALSE}
redFlags(proofed_data, type = "field", threshold = 0.3)
```
